A Cost-Aware Approach to Adversarial Robustness in Neural Networks

### 2024-09-11 cover_letter.tex
letter update

I am writing you on behalf of the authors of \textit{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}, which is the attached manuscript.  In this work, we developed a cloud-native methodology for quickly and precisely modelling the effect of model covariates using accelerated failure time models and a multi-objective search to minimize training cost while maximizing model accuracy. Not only do we provide a detailed outline and related source code, but we show the surprising result that smaller, more power-efficient GPUs create models that are more robust and more cost effective than models built on hardware that is advertised as being more capable.

% You can add something about why we submit to this journal (showing that we are in scope and that we think highly of the journal) and that we look forward to a swift processing of the manuscript.)

>>>>

I am writing you on behalf of the authors of \textit{A Cost-Aware Approach to Adversarial Robustness in Neural Networks}, which is the attached manuscript.  In this work, we developed a cloud-native methodology for quickly and precisely modelling the effect of model covariates using accelerated failure time models and a multi-objective search to minimize training cost while maximizing model accuracy. Not only do we provide a detailed outline and related source code, but we show the surprising result that smaller, more power-efficient GPUs create models that are more robust and more cost effective than models built on hardware that is advertised as being more capable. We targeted your venue not only because of its open-access policies, but because we feel that the problems of deploying and verifying neural networks can be abstracted away from the expertise required for their operation. That is to say, this technique and this text were developed and written for cloud-focused system administrators and computer scientists, not machine learning specialists and mathematicians. Finally, we think that the surprising result is worth communicating to this audience in particular since our results show how to significantly reduce infrastructure costs and power requirements for image classification systems without sacrificing quality.
